Review: The Prevalence of Adaptive Introgression in Crop Histories

### 2018-06-27 paper.tex
edits throughout

Application of these approaches, in combination with population genetic statistics to detect selection, suggest that introgression can play an adaptive role.
For example, based on sequence divergence methods, introgression has been detected in \emph{Mimulus} (\emph{i.e.}, monkeyflower) species and appears to play a role in both adaptation to pollinator preference and speciation \cite{Stankowski2015}.
Likewise, the HAPMIX chromosome painting method was applied by Jeong et al. \cite{jeong2014} to detect introgression in human populations from the Nepalese Sherpa to Tibetans at loci controlling high altitude adaptation (reviewed in \cite{Racimo2015}).
Finally, the ABBA-BABA statistic has revealed introgression at wing coloration loci conferring M\"{u}llerian mimicry across butterfly species \cite{heliconius2012}.

@@

Populations of \emph{mexicana} cannot be found outside the highlands of Mexico, yet maize has colonized and adapted to high elevation in a number of other regions.
A recent study \cite{wang2017} employed the ABBA-BABA and $\hat{f_{d}}$ statistics to evaluate if maize with \emph{mexicana} introgression was transferred to other highland regions or whether highland adaptation was obtained \emph{de novo} outside of Mexico.
Overall, analyses revealed that  \emph{mexicana} introgression was pervasive in maize from Mesoamerican high elevation regions (the highlands of Mexico, Guatemala, and the southwestern United States), but more distant high elevation regions (\emph{e.g.,} the Andes) showed no \emph{mexicana} ancestry.
Maize from the lowlands of northern South America appears to have been derived from Mesoamerican lowland maize and high elevation adaptation in Andean maize likely occurred \emph{de novo} from this genetic base.

@@

While the four crop systems described in detail here represent particularly well documented examples of adaptive wild introgression, given their similar histories, many additional crops have likely benefited from beneficial wild-to-crop gene flow during post-domestication expansion (\textbf{Table 1}).
Across these four cases studies, potential generalities can be observed.
Data thus far indicate that wild introgression is often local or regional in its extent, but that, in certain cases (\emph{e.g.}, \emph{mexicana} haplotypes detected in maize landraces from the Guatemalan or southwestern U.S. highlands), newly introgressed wild haplotypes can be disseminated more broadly.
Additionally, when functional information is evaluated, as in the maize and potato studies, introgression has been found to occur at loci conferring adaptation to novel conditions not found in a crop's center of origin.
Beyond these observations associated with post-domestication adaptation, pervasive wild-to-crop gene flow bears meaningfully on the study of domestication.

>>>>

Application of these approaches, in combination with population genetic statistics to detect selection, suggest that introgression can play an adaptive role.
For example, based on sequence divergence methods, introgression has been detected in \emph{Mimulus} (\emph{i.e.}, monkeyflower) species and appears to play a role in both adaptation to pollinator preference and speciation \cite{Stankowski2015}.
Likewise, the HAPMIX ancestry deconvolution method was applied by Jeong et al. \cite{jeong2014} to detect introgression in human populations from the Nepalese Sherpa to Tibetans at loci controlling high altitude adaptation (reviewed in \cite{Racimo2015}).
Finally, the ABBA-BABA statistic has revealed introgression at wing coloration loci conferring M\"{u}llerian mimicry across butterfly species \cite{heliconius2012}.

@@

Populations of \emph{mexicana} cannot be found outside the highlands of Mexico, yet maize has colonized and adapted to high elevation in a number of other regions.
Wang and co-authors \cite{wang2017} employed the ABBA-BABA and $\hat{f_{d}}$ statistics to evaluate if maize with \emph{mexicana} introgression was transferred to other highland regions or whether highland adaptation was obtained \emph{de novo} outside of Mexico.
Overall, analyses revealed that  \emph{mexicana} introgression was pervasive in maize from Mesoamerican high elevation regions (the highlands of Mexico, Guatemala, and the southwestern United States), but more distant high elevation regions (\emph{e.g.,} the Andes) showed no \emph{mexicana} ancestry.
Maize from the lowlands of northern South America appears to have been derived from Mesoamerican lowland maize and high elevation adaptation in Andean maize likely occurred \emph{de novo} from this genetic base.

@@

The four crop systems described in detail here represent particularly compelling examples of putatively adaptive wild introgression.
However, given their similar histories, many additional crops have likely benefited from wild-to-crop gene flow during post-domestication expansion (\textbf{Table 1}).
Across these four cases studies, potential generalities can be observed.
Data thus far indicate that wild introgression is often local or regional in its extent, but that, in certain cases (\emph{e.g.}, \emph{mexicana} haplotypes detected in maize landraces from the Guatemalan or southwestern U.S. highlands), newly introgressed wild haplotypes can be disseminated more broadly.
Additionally, when functional information is evaluated, as in the maize and potato studies, introgression has been found to occur at loci conferring adaptation to novel conditions not found in a crop's center of origin.
Beyond these observations associated with post-domestication adaptation, pervasive wild-to-crop gene flow is also relevant to the study of domestication itself.
